Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-13 doc/PRF2022/PRF_main.tex
started "results" section

\subsection{Mobility problem}
A suspension of $N_b$ Janus particles is immersed in a vicsous solvent.
The domain $\Omega(t) \subset \mathbb{R}^2$ denotes the solvent phase
where $t$ is time.
The particles are disks of radius $c$ with center $\aa_i$ and
orientation $\theta_i$ relative to a fixed horizontal axis.  
The boundary of the $\Omega$ is $\bd\Omega = \Gamma_1 \cup
\cdots \cup \Gamma_{N_b}$, where $\Gamma_i$ is the boundary of Janus
particle $i$. Assuming inertial terms are
negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0},     && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent,
$p$ is the pressure, $\uu_\infty$ is the
background flow, and $\mu$ is the constant viscosity.
On the boundaries, the solvent
velocity satisfies a no-slip boundary condition for a rigid body motion
\begin{equation}
  \label{eq:rigid-vel}
  \vv_i + \omega_i (\xx - \aa_i)^\perp = \uu(\xx), 
    \quad \xx \in \Gamma_i,
\end{equation}
where $\vv_i$ is the translational velocity, $\omega_i$ is the
angular velocity, and
$\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

To close the system \eqref{eq:stokes}-\eqref{eq:rigid-vel},
we use
\begin{equation}
  \label{eq:force}
  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i, \quad
  \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
  (\ssigma \cdot \nnu) \, \dif s = T_i,
  \quad i=1,\ldots,N_b,
\end{equation}
where $\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
are interparticle forces and torques. 
Here $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor) and
$\nnu$ is the particle outward normal.

To get $\FF_i$ and $T_i$,
the particles minimizes the free energy
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
Here, $u(\xx,t)$ is an order parameter for the structure of water
in the presence of hydrophobic surfaces,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
We model water structure
using the screened Laplace equation boundary value problem:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ represents the degree of hydrophobicity
the particle (Figure~\ref{fig:bcs}).

Variation of the
the free energy \eqref{eq:free_energy}
provides
\begin{equation}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$. The term 
$
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
$
is the hydrophobic stress it is derived from 
variation of the domain as described in ~\cite{Fu2018_SIAM}.

The dimensionless repulsion profile $P$
takes the form
$P(s) = 1 - \sin(\pi s/2)$ for $0 \leq s < 1$
and $P(s) = 0$ for $1 \leq s < \infty$.
As such, only those particles within
a $\rho_0$-tubular neighborhood of $\Gamma_i$
contribute to repulsion.  The parameter $M$ is the repulsion modulus.

\subsection{Boundary integral represenation and time stepping}
We recast \eqref{eq:stokes}-\eqref{eq:rigid-vel} and \eqref{eq:SL}
as boundary integral equations (BIEs) and discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
To express the solution of \eqref{eq:SL},
we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
, \quad \xx \in \Omega,
\end{align}
where $G(\xx)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL}
and where $\sigma$ is a scalar-valued density function.
The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
For the velocity, we use the representation  
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
with the vector-valued density function $\eeta$,
Stokeslet 
$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr \otimes \rr}{|\rr|^2}\right)$,
and Rotlet
$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$.

Finally, together with \eqref{eq:velocity},
\eqref{eq:stokes}-\eqref{eq:rigid-vel} become 
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:mobility}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$.

@@

Once determined the translational and angular velocities $\vv_i, \omega_i$
have been determined, a second-order Adams-Bashforth scheme updates the particle
positions and orientations:
\begin{equation}
  \label{eq:adams-bashforth}
  \begin{aligned}
    \aa_i(t_{n+2}) &=
\aa_i(t_{n+1})
+ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
    \theta_i(t_{n+2}) &=
\theta_i(t_{n+1})
+ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
  \end{aligned}
\end{equation}

@@

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
The present paper considers boundary condition of the form
\begin{equation}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{equation}
where $\alpha$ is the angle between $\xx - \aa_i$ and the particle director
$\dd_i = (\cos \theta_i, \sin \theta_i)$.
We refer to the side of the particle where $\alpha = 0$ as the head and the
side where $\alpha = \pi$ as the tail. 
The boundary conditions are
normalized so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.

To see the effect of the shift parameter $b$, we simulate the dynamics of
60 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
There are three cases:
(i) $b = 1$, bilayers,
(ii) $b = 2$, multilamellar
and (iii) $b = 0$, striated.

Case (i), $b = 1$, mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic tail,
and takes the maximum value $a$ on the
hydrophobic head. 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)).

In case (ii), $b = 1$ the boundary condition is positive everywhere.
It takes the maximum value $3a$ on head where $\alpha = 0$ and the
minimum value $a$ on the tail side where $\alpha = \pi$. This way,
both sides of the Janus particle are hydrophobic but
moreso on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers also adhere to one another 
forming multilamella structures. Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with 2 layers. The number of folds depends on several factors,
for instances, number of particles and intial configurations.

A water structure with
positive/negative charge is possible in case (iii), $b = 0$
\cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
It is worth noting that in the dipolar molecules modeled by
Laplace equation, the equilibrium configurations consist of strands,
rather than a patch, of particles and also have
alternating orientations \cite{}. Unlike the electrical case, though,
the chains form striated layers
where the particles lie on a 
grid and the orientations alternate between layers (Figure~\ref{fig:relax}(d)).

\section{Measuring deformation}
We use the free energy $F$,
the Euclidean distance matrix $D(t)$,
and a scalar order parameter $S_{2}(t)$ to measure
the deformation of particle configurations under background flows.

We simplify the
form of the free energy \eqref{eq:free_energy}
using integration by parts and \eqref{eq:SL}
to obtain
\begin{equation}
\label{eq:free_energy2}
F[u] = -\gamma
\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
\end{equation}
%
This is simpler because the boundary data $g$ are known.
Evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
directly, however,
involves calculating a quadruple layer potential which has a
well-known obstacle in numerical implementation.
To overcome this obstacle, we use
%
\begin{equation}
\label{eq:normal_deriv}
\nabla u(\xx) \cdot \nnu(\xx)=
%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
\end{equation}
%
Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
See the Appendix section \ref{sec:appendix} for the proof and details.
Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
leads to single layer integral which is more straightforward to evaluate and we compute the
arclength derivative using spectrally accurate Fourier transform.

The $N_b$ by $N_b$ Euclidian distance matrix is 
\begin{equation}
  \label{eq:EDM}
[D(t)]_{ij} = \|\aa_{i} - \aa_{j}\|, \quad i, j = 1, \dots, N_b.
\end{equation}
For weak background flow strengths, the deformation in particle
configurations will be relatively small and the collection of
particles behaves as a rigid body i.e., $\|D(t) - D(0)\| \ll 1$.

To study the change in orientational order, we use the scalar order parameter 
\begin{equation}
  \label{eq:S2}
S_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta$ is a circular mean defined as the
orientation of the largest eigenvalue eigenvector of the projection 
$\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
A value $S_2(t) = 1$ indicates a complete orientational order where all particle
directors lie on a common axis. A value far from 1 indicated disorder.

It turns out that $S_2$ is an inadequate measure of order for the bilayer and
multilamellar configurations.  For example, the directors of a circular
bilayer vesicle are uniformly distributed along a circle, even though
there is a strong orientational order between neighboring particles.
To account for these latter cases, we use
\begin{equation}
  \label{eq:localS2}
\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
\end{equation}
where $\bar \theta_i$ is the circular mean restricted to particles
indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
isolated and has no neighbors within a distance $4c$, then we exclude it from
the sum \eqref{eq:localS2}.

@@

@@

\begin{figure}
  \begin{center}
  \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_Energy_LsFs}
    \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_MSD_LsFs}
  \end{center}
    \caption{ A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$. We tune the length scale parameters, radius, $\rho$ and $\rho_0$, by $\pm 5\%$ and the force scale parameters, $\gamma$ and $M$, by $\pm 5\%$.    }
\end{figure}

>>>>

\subsection{Mobility problem}
A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
The domain $\Omega(t) \subset \mathbb{R}^2$ is the solvent phase
and $t$ is time.
The particles are disks of radius $c$, center $\aa_i$, and
orientation $\theta_i$ relative to the horizontal axis.  
The boundary of the $\Omega$ is $\bd\Omega = \Gamma_1 \cup
\cdots \cup \Gamma_{N_b}$, where $\Gamma_i$ is the boundary of Janus
particle $i$. Assuming inertial terms are
negligible, we have 
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0},     && \xx \in \Omega, \\
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity of the solvent,
$p$ is the pressure, $\uu_\infty$ is the
background flow velocity, and $\mu$ is the constant viscosity.
The solvent velocity satisfies a no-slip boundary
condition for a rigid body motion
\begin{equation}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{equation}
where $\vv_i$ is the translational velocity, $\omega_i$ is the
angular velocity, and
$\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

To close the system \eqref{eq:stokes}-\eqref{eq:rigid-vel},
we use
\begin{equation}
  \label{eq:force}
  \int_{\Gamma_i} \ssigma \cdot \nnu \, \dif s = \FF_i, \quad
  \int_{\Gamma_i} (\xx - \aa_i)^\perp \cdot 
  (\ssigma \cdot \nnu) \, \dif s = T_i,
  \quad i=1,\ldots,N_b,
\end{equation}
where $\FF_i \in \mathbb{R}^2$ and $T_i \in \mathbb{R}$
are interparticle forces and torques. 
Here $\ssigma = -p \mathbf{I} + \mu \left(\nabla \uu + \nabla \uu^T
\right)$ is the hydrodynamic stress tensor (pressure tensor), and
$\nnu$ is the particle outward normal.

To get $\FF_i$ and $T_i$,
the particles minimize the free energy
\begin{equation}
\label{eq:free_energy}
F = \gamma
\int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2
\,d\xx
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right), \quad
\end{equation}
Here, $u(\xx,t)$ is an order parameter for the structure of water,
$\rho$ is a decay length, and $\gamma$ is an interfacial tension. 
We model water structure
using the screened Laplace equation boundary value problem:
\begin{gather}
  \label{eq:SL}
  -\rho^2 \Delta u + u = 0,\quad \xx \in \Omega, \\
  u = g, \quad \xx \in \bd\Omega, \quad 
  u \rightarrow 0, \quad |\xx| \rightarrow \infty.
\end{gather}
The boundary condition $g$ gives the degree of hydrophobicity
the particle-solvent interface (Figure~\ref{fig:bcs}).

Variation of the
the free energy \eqref{eq:free_energy}
provides
\begin{equation}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s, 
\end{equation}
for $i = 1,\dots,N_b$. The term 
$
\mathbf{T}
= \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
$
is the hydrophobic stress identified in ~\cite{Fu2018_SIAM} 
and derived by variation of the domain techniques.

The dimensionless repulsion profile $P$
takes the form
$P(s) = 1 - \sin(\pi s/2)$ for $0 \leq s < 1$
and $P(s) = 0$ for $1 \leq s < \infty$.
As such, only those particles within
a distance $\rho_0$ of $\Gamma_i$
contribute to repulsion.
The parameter $M$ is the repulsion modulus.

We use the parameters $\mu = 1$ cP, $\gamma = 4$ pN nm$^{-1}$,
$\rho = 5$ nm, $c = 1.25$ nm, $M = 2$ pN, and $\rho_0 = 0.5$ nm.
\subsection{Boundary integral represenation and time stepping}
We recast \eqref{eq:stokes}-\eqref{eq:rigid-vel} and \eqref{eq:SL}
as boundary integral equations (BIEs) and discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
To express the solution of \eqref{eq:SL},
we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\bf x}) = \DD[\sigma](\xx) = \int_\Gamma \frac{\partial G(\xx-\yy)}{\partial \nnu_\yy}\sigma(\yy)\, \dif s_\yy
, \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental solution to the screened Laplace equation \eqref{eq:SL},
$K_0$ is the zeroth-order modified Bessel function of the first kind,
and $\sigma$ is a scalar-valued density function.
The subscript in $\dif s_\yy$ denotes integration with respect to $\yy \in \Gamma$. 
For the velocity, we use the representation [REF]
\begin{align}
  \label{eq:velocity}
  \uu(\xx) = \uu_\infty(\xx) + \DD[\eeta](\xx) + 
    \sum_{i=1}^{N_b} \left(\SS(\xx,\aa_i) \cdot \FF_i + 
    \RR(\xx,\aa_i) T_i\right), \quad \xx \in \Omega,
\end{align}
with the vector-valued density function $\eeta$,
Stokeslet 
$\SS(\xx,\aa_i) = \frac{1}{4\pi} \left(-\log |\rr|\mathbf{I} + \frac{\rr \otimes \rr}{|\rr|^2}\right)$,
and Rotlet
$\RR(\xx,\aa_i) = \frac{1}{4\pi} \frac{\rr^\perp}{|\rr|^2}$,
$\rr = \xx - \aa_i$ [REF].

Finally, together with \eqref{eq:velocity},
\eqref{eq:stokes}-\eqref{eq:rigid-vel} become 
\begin{alignat}{3}
  \label{eq:vel_BLM_rep}
  \vv_i + \omega_i (\xx - \aa_i)^\perp &= \uu_\infty(\xx)
    -\frac{1}{2} \eeta(\xx) + \DD[\eeta](\xx) 
    + \sum_{j=1}^{N_b} 
    \left(\SS(\xx,\aa_j) \cdot \FF_j + \RR(\xx,\aa_j) T_j\right),\\
  \label{eq:mobility}
  \int_{\Gamma_i} \eeta \, \dif s &= \mathbf{F}_i, \quad
  \int_{\Gamma_i} \eeta \cdot (\xx-\aa_i)^\perp \, \dif s = T_i,
\end{alignat}
for $\xx \in \Gamma_i$ and $i = 1,\dots,N_b$ [REF].

@@

Once the translational and angular velocities $\vv_i, \omega_i$
have been determined, a second-order Adams-Bashforth scheme updates the particle
positions and orientations:
\begin{equation}
  \label{eq:adams-bashforth}
  \begin{aligned}
    \aa_i(t_{n+2}) &=
\aa_i(t_{n+1})
+ \tfrac{3}{2}\Delta t \vv_i(t_{n+1})
- \tfrac{1}{2}\Delta t \vv_i(t_{n}),\\
    \theta_i(t_{n+2}) &=
\theta_i(t_{n+1})
+ \tfrac{3}{2}\Delta t \omega_i(t_{n+1})
- \tfrac{1}{2}\Delta t \omega_i(t_{n}).
  \end{aligned}
\end{equation}

@@

\section{Equilibrium configurations}
\subsection{Boundary conditions and normalization}
The present paper considers boundary condition of the form
\begin{equation}
  \label{eq:bc-type}
g(\xx) = a(b + \cos \alpha),\quad a = (\pi c(2b^2 + 1))^{-1/2},\quad \xx \in \Gamma_i,
\end{equation}
where $\alpha$ is the angle between $\xx - \aa_i$ and the particle director
$\dd_i = (\cos \theta_i, \sin \theta_i)$.
The parameter $a$ normalizes the boundary conditions 
so that $\int_{\Gamma_i} g^2(\xx) \, \dif s = 1$.
We refer to the side of the particle where $\alpha = 0$
as the tail and the side where $\alpha = \pi$ as the head.

To see the effect of the shift parameter $b$, we simulate the dynamics of
198 particles in a quiescent flow as shown in Figure~\ref{fig:relax}.
Three distinct configurations emerge:
(i) bilayers for $b = 1$, 
(ii) multilamellar for $b = 2$, and 
(iii) striated for $b = 0$.

Case (i) with $b = 1$, mimicks an amphiphilic particle.
The boundary condition $g$ is everywhere nonnegative,
takes the value $0$ on the
hydrophilic head,
and takes the maximum value $a$ on the
hydrophobic tail. 
The interaction is attractive, and particles collectively orient their
hydrophobic sides to form bilayers  (Figure~\ref{fig:relax}(b)).

In case (ii) with $b = 1$, the boundary condition is positive everywhere.
It takes the maximum value $3a$ on tail and the
minimum value $a$ on the head side. 
Both sides of the Janus particle are hydrophobic but
moreso on the $\alpha = 0$ side.  
Over a short time scale, these particles also self-assemble into bilayers. But unlike for case (i),
the heads are also hydrophobic and so in the long-time dynamics
these bilayers also adhere to one another 
forming multilamella structures. Figure~\ref{fig:relax}(c), for example, shows a
multilamellar structure with 2 layers.
At equilibrium, the number of folds depends primarily on the number of particles.

A water structure with
positive/negative charge is possible in case (iii), $b = 0$
\cite{MaRa76, Ma77}.
Here, the head repels the tail of other particles
and the particles initially form chains with their directors perpendicular
to the length of the chain.  
The chains form stria
where the particles lie on a 
grid and the orientations alternate between layers (Figure~\ref{fig:relax}(d)).

The equilibrium configurations for case (ii) and (iii) are used as initial data in the
background flow simulations found in Section \ref{sec:results}.
In case (i), there are several connected
components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
To have a single, coherent vesicle (i), we reinitialize
the case (i) particles in the form of a ring and run the relaxation procedure once more.
\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
    The free energy \eqref{eq:free_energy} is decreasing
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations Figure \ref{fig:relax}b--c, respectively. 
    The red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles.
  }
\end{figure}

\section{Measuring deformation}
We use the free energy $F$,
a Euclidean distance-based measure $d(t)$,
and a scalar order parameter $S_{2}(t)$ to measure
the deformation of particle configurations under background flows.

First, we must simplify the
form of the free energy \eqref{eq:free_energy}
using integration by parts and \eqref{eq:SL}
to obtain
\begin{equation}
\label{eq:free_energy2}
F[u] = -\gamma
\int_{\Gamma} \rho g \nabla u \cdot \nnu \,\dif s
+ \frac{M}{2}
\sum_{j \neq i} 
P\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right).
\end{equation}
%
Here, we have substituted $g$ for $u$ since the boundary values are given.
However, evaluating $\nabla u \cdot \nnu$ on $\Gamma$ based on \eqref{eq:SL_BIE}
involves calculating a quadruple layer potential which has a
well-known obstacle in numerical implementation.
To overcome this obstacle, we use
%
\begin{equation}
\label{eq:normal_deriv}
\nabla u(\xx) \cdot \nnu(\xx)=
%\frac{\partial}{\partial \nnu_\xx} \DD[\sigma](\xx) =
-\frac{1}{\rho^2} {\bf t}_\xx\cdot \SSS[\sigma{\bf t}](\xx)
+ \frac{\dif}{\dif s}\SSS\left[\frac{\dif \sigma}{\dif s}\right](\xx), \quad \xx \in \Gamma.
\end{equation}
%
Here, ${\bf t}(\xx)$ is the tangent vector and $\dif/\dif s$ is the arclength derivative.
See the Appendix section \ref{sec:appendix} for the proof and details.
Substituting \eqref{eq:normal_deriv} into \eqref{eq:free_energy2} for the normal derivative
leads to single layer integral which is more straightforward to evaluate and we compute the
arclength derivative using spectrally accurate Fourier transform.
We have validated the form of \eqref{eq:normal_deriv} by extrapolating 
the primal energy \eqref{eq:free_energy} along test curves placed slightly
outside the particles.

The Euclidian distance matrix is the $N_b \times N_b$ matrix 
$[D(t)]_{ij} = \|\aa_{i} - \aa_{j}\|$ for $i, j = 1, \dots, N_b$
To measure positional order, we use
\begin{equation}
\label{eq:EDM}
d(t) = \frac{1}{N_b^2}\|D(t) - D(0)\|
\end{equation}
where $\| \cdot \|$ is the Frobeneous norm.
For weak background flow strengths, the deformation in particle
configurations will be relatively small and the collection of
particles behaves as a rigid body i.e., $d(t) \ll 1$.

To study orientational order, we use the scalar order parameter 
\begin{equation}
  \label{eq:S2}
S_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b} \frac{1}{2}(3\cos^2(\theta_i - \bar \theta) - 1).
\end{equation}
Here $\bar \theta$ is a circular mean defined as the
orientation of the largest eigenvalue eigenvector of 
$\dd_1\dd_1^\top + \dots + \dd_{N_b}\dd_{N_b}^\top$.
A value $S_2(t) = 1$ indicates a complete orientational
order where all particle directors lie on a common axis e.g.,
two parallel vectors with possibly opposite direction are ordered. 
A value far from 1 indicates disorder.

The measure $S_2$ is an inadequate for the bilayer and
multilamellar structures.  For example, the directors of a circular
bilayer vesicle are uniformly distributed along a circle, even though
there is a strong orientational order between neighboring particles.
To account for these latter cases, we use
\begin{equation}
  \label{eq:localS2}
\tilde{S}_2(t) = \frac{1}{N_b} \sum_{i=1}^{N_b}
\frac{1}{2}(3\cos^2(\theta_i - \bar \theta_i) - 1).
\end{equation}
where $\bar \theta_i$ is the circular mean restricted to particles
indexed by $j$ for which $\|\aa_i - \aa_j\| < 4c$. In practice, if a particle is
isolated and has no neighbors within a distance $4c$, then we exclude it from
the sum \eqref{eq:localS2}.

\section{Results}
\label{sec:results}
\begin{figure}
\caption{\label{fig:ves_shear} A vesicle in shear flow}
\end{figure}
\begin{figure}
\caption{\label{fig:ves_shear} A vesicle in Taylor-Green flow}
\end{figure}
\subsection{Boundary condition (i):   bilayer configurations}
The vesicle in a shear flow undergoes the familiar tank-treading deformation.
Our previous paper \cite{Fu2022_JFM} studied the geometry,
intermonolayer slip, and critical shear rates $\gamma^*$
for vesicles comprised of amphiphilic Janus particles.

The vesicle is subject to a shear background flow
\begin{equation}
\uu_\infty(\xx) = \dot\gamma ({\bf e}_y\cdot\xx){\bf e}_x,
\end{equation}
%
where $\dot\gamma$ is the shear rate. Figure~\ref{fig:shear_1} (a)--(c)
shows snapshots of the vesicle when $\dot\gamma= ... $ is
below the critical shear rate $\dot \gamma_* = ...$
Here, the free energy and order parameter are more or less constant
(Figure \ref{fig:BC1_shear}ab, solid curves).  The is a slight upward shift
in $d(t)$ (Figure \ref{fig:BC1_shear}c, solid curve) due to relative
displacement as the two leaflets slide past one another.

In, Figure~\ref{fig:shear_2} (a)--(c), 
$\dot\gamma= ...$ is above the critical shear rate,
and there is a jump in energy (Figure \ref{fig:BC1_shear}a, dashed curve)
due to the breaking of the vesicle into two components.  
There is greater variation in the order parameter $\tilde{S}_2(t)$ as well
with a baseline value around $0.7$
(Figure \ref{fig:BC1_shear}b, dashed curve).The oscillations occur due to the
orbit of the two bilayer components, and $\tilde{S}_2(t)$ increases
to about $0.9$ when the components are nearly parallel and slide past one another.
Positional order, however, diverges since the two component configuration
is uncorrelated to the initial circular configuration (Figure \ref{fig:BC1_shear}c, dashed curve).

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.1\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
\end{figure}

The Taylor-Green (TG) background flow is
\begin{equation}
  \uu_\infty(\xx) = V_0 \left(-\cos({\bf e}_x\cdot\xx/l)\sin({\bf e}_y\cdot\xx/l){\bf e}_x
  +\sin({\bf e}_x\cdot\xx/l)\cos({\bf e}_y\cdot\xx/l){\bf e}_y\right).
\end{equation}
where $l$ sets the size of the rotating cells and $V_0$ is the flow strength. 
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.24\textwidth]{shear_0.png}
  \includegraphics[width=0.24\textwidth]{shear_1000.png}
  \includegraphics[width=0.24\textwidth]{shear_2000.png} 
  \includegraphics[width=0.24\textwidth]{shear_2000.png} \\
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.32\textwidth]{TG_0.png}
  \includegraphics[width=0.32\textwidth]{TG_2500.png}
  \includegraphics[width=0.32\textwidth]{TG_5000.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
\end{figure}
\subsection{Boundary condition (ii):  multilamellar configurations}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.21\textwidth]{shear_checker_0.png}
  \includegraphics[width=0.21\textwidth]{shear_checker_250.png}
  \includegraphics[width=0.21\textwidth]{shear_checker_500.png}
  \includegraphics[width=0.21\textwidth]{shear_checker_750.png} \\
%  \includegraphics[width=0.4\textwidth]{lambda_fig1.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(ii) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}
%
\subsection{Boundary condition (iii): striated configurations}

\section{Discussion}
\begin{figure}
  \begin{center}
  \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_Energy_LsFs}
    \includegraphics[height=0.2\textheight]{multilamellar_shear0p1_MSD_LsFs}
  \end{center}
    \caption{ A multi-lamellar structure in a shear flow when the shear rate is $\dot\gamma=0.1$. We tune the length scale parameters, radius, $\rho$ and $\rho_0$, by $\pm 5\%$ and the force scale parameters, $\gamma$ and $M$, by $\pm 5\%$.    }
\end{figure}

It is worth noting that in the dipolar molecules modeled by
Laplace equation, the equilibrium configurations consist of strands,
rather than a patch, of particles and also have
alternating orientations \cite{}.

@@

\end{document}

@@
